Demo of Random Forest Method Ver 1.0.a.

### 2019-02-21 docs/hiding/Naive_bayes_V2r_2b.Rmd
update

---
title: "Naive Bayes Workflow Ver 2.0.r"
author: "Dan Johnson"
date: "2/14/2019"
output: html_document
---

@@

##Summary
This is **Version 2r.2a** of the basic workflow for classifying TA comments using a naive Bayes model. It pre-processes text using the same command set as Ver 2.0.b. The "r" designates this version has been modified to be able to randomize which rows are selected for training and test datasets.

This updated version refines the final output tables so they are more informative.

@@

##Version 2.0.r of Naive Bayes (NB) Protocol
###Initial Data Input
```{r}
#Read in TA comments from CSV file.
base_dataVERB <- read_csv(file='data/coded_full_comments_dataset_Spring18anonVERB.csv')
```

###Extract, Organize Data Subset
Extract comments and classification data subset
```{r}
#Select rows representing the sub-groups to compare. 
comments_subsetVERB <- filter(base_dataVERB,code.subject=="1_basic"|code.subject=="2_writing"|code.subject=="3_technical"|code.subject=="4_logic")

#Reduce larger dataframe to 2 required columns of data, and put columns in order needed.
comments_rawVERB <- comments_subsetVERB %>% select(23,24,22)

#Rename the columns.
names(comments_rawVERB)[1] <- "subject"
names(comments_rawVERB)[2] <- "structure"
names(comments_rawVERB)[3] <- "text"

#Change "subject" element from character to a factor for analysis.
comments_rawVERB$subject <- factor(comments_rawVERB$subject)
str(comments_rawVERB$subject)
table(comments_rawVERB$subject)
```

```{r}
#Change "structure" element from character to a factor for analysis.
comments_rawVERB$structure <- factor(comments_rawVERB$structure)
str(comments_rawVERB$structure)
table(comments_rawVERB$structure)
```

```{r}
#Generate a vector of ~10,000 numbers (be sure it can be generated consistently)
#Adjust the number so it matches the number of rows in the original data frame
#Next, set the seed for random numbers, and randomize the order of the vector
vector <- 1:9340
set.seed(567) #change this seed value, and the data are randomized in a new sequence.
vector <- sample(vector)
glimpse(vector)
```

```{r}
#Append the vector as a new column to "comments_rawVERB" with name "randomizer"
#Sort rows of dataframe according to "randomizer" column using dplyer 'arrange' function. 
comments_rawVERB$randomizer <- c(vector)
comments_rawVERB_R <-comments_rawVERB %>% arrange(randomizer)
print(comments_rawVERB_R)

@@

```{r}
#Convert text to all lower case letters.
comments_corpus_cleanVERB_R <- tm_map(comments_corpusVERB_R, content_transformer(tolower))

#Remove punctuation using the "removePunctuation" function. 
#This step removes evidence of questions, so may remove data.
#THIS ALSO REMOVES EVIDENCE OF POINTER ITEMS
comments_corpus_cleanVERB_R <- tm_map(comments_corpus_cleanVERB_R, removePunctuation)

#Remove numerals. 
#I am not sure this is beneficial; does it remove evidence indicating technical comments?
comments_corpus_cleanVERB_R <- tm_map(comments_corpus_cleanVERB_R, removeNumbers)

#Stopword removal. 
#This is a standard cleanup step, but again may remove useful terms.
#The "stopwords" file is a convention; other files can be substituted for it
comments_corpus_cleanVERB_R <- tm_map(comments_corpus_cleanVERB_R, removeWords, stopwords())

@@

comments_dtm_1gram <- DocumentTermMatrix(comments_corpus_cleanVERB_R, control=list(tokenize = NLP_Tokenizer))
comments_dtm_1gram_tidy <- tidy(comments_dtm_1gram)
inspect(comments_dtm_1gram)
```

@@

This code uses the comments in the order they are listed in the original file. Block for randomizing them was done earlier.
```{r}
comments_dtm_train <- comments_dtm_1gram[1:7005, ]
comments_dtm_test <- comments_dtm_1gram[7006:9340, ]
comments_dtm_all <- comments_dtm_1gram[1:9340, ]
```

Save vectors labeling rows in the training and testing vectors
```{r}
comments_train_labels_subject <- comments_rawVERB_R[1:7005, ]$subject
comments_test_labels_subject <- comments_rawVERB_R[7006:9340,]$subject
comments_all_labels_subject <- comments_rawVERB_R[1:9340,]$subject
```

```{r}
comments_train_labels_structure <- comments_rawVERB_R[1:7005, ]$structure
comments_test_labels_structure <- comments_rawVERB_R[7006:9340,]$structure
comments_all_labels_structure <- comments_rawVERB_R[1:9340,]$structure
```

Make sure that the proportion of each sub-category is similar in the training and testing data sets.
```{r}
prop.table(table(comments_train_labels_subject))
prop.table(table(comments_test_labels_subject))
prop.table(table(comments_all_labels_subject))
```

```{r}
prop.table(table(comments_train_labels_structure))
prop.table(table(comments_test_labels_structure))
prop.table(table(comments_all_labels_structure))
```

@@

Limit Document Term Matrix to only include words in the comments_freq_words vector. Using all the rows, but we want to limit the columns to these words in the frequency vector.
```{r}
comments_dtm_freq_train <- comments_dtm_train[ , comments_freq_words]
comments_dtm_freq_test <- comments_dtm_test[ , comments_freq_words]
comments_dtm_freq_all <- comments_dtm_all[ , comments_freq_words]
```

The basic e1071 naive bayes classifier works with categorical features, so the matrix must be converted "yes" and "no" categorical variables. This is done using a **convert_counts function** and applying it to the data. This replaces values greater than 0 with yes, and values not greater than 0 with no. 
```{r}
convert_counts2 <- function(x) {
  x <- ifelse(x > 0, "Yes", "No")
}
```

The resulting matrices have cells indicating "yes" or "no" if the word represented by the column appears in the text comment represented by the row.

```{}
# Function to KEEP word frequencies while still using the same variable names and code structure. The resulting matrices have cells with word frequencies instead.
convert_counts2 <- function(x) {
  y <- x
}
```

```{r}
comments_train <- apply(comments_dtm_freq_train, MARGIN = 2, convert_counts2)
comments_test <- apply(comments_dtm_freq_test, MARGIN = 2, convert_counts2)
comments_all <- apply(comments_dtm_freq_all, MARGIN = 2, convert_counts2)
```

@@

###Train Model, Predict, Evaluate for Subject
This block uses the e1071 package to implement Naive Bayes algorithm on the data, and predict whether a message is likely to be in group 1_basic, 2_writing, 3_technical, or 4_logic. It evaluates the prediction with the actual data using a crosstable from the gmodels package.
```{r}
comments_classifier_subject <- naiveBayes(comments_train, comments_train_labels_subject, laplace=1)
comments_test_pred_subject <- predict(comments_classifier_subject, comments_test)
comments_all_pred_subject <- predict(comments_classifier_subject, comments_all)

# Create a truth table by tabulating the predicted class labels with the actual class labels 
table("Predictions"= comments_test_pred_subject,  "Actual" = comments_test_labels_subject )

table("Predictions"= comments_all_pred_subject,  "Actual" = comments_all_labels_subject )

#table("Predictions2"= comments_test_pred_structure,  "Actual" = comments_test_labels_structure )

@@

# Prepare the confusion matrix. 
conf.mat <- confusionMatrix(comments_test_pred_subject, comments_test_labels_subject)
conf.mat2 <- confusionMatrix(comments_all_pred_subject, comments_all_labels_subject)

# This print-out has both the overall and by-group accuracy values.
conf.mat2
print (line)

# This print-out has by-group accuracy values in a single column. 
conf.mat2$byClass
print (line)

# This print-out is a single line table with overall accuracy, kappa, lower and higher limits of accuracy, accuracy null value, P value for accuracy, and Mcnemar P value.
conf.mat2$overall
print (line)

# This outputs JUST the overall accuracy value. 
conf.mat2$overall['Accuracy']

@@

```{r}
#Creates a data frame that compares predicted and actual labels for subject and structure
tallyall <- data.frame("text"=c(comments_rawVERB_R[1:9340,]$text),"subject_label"=c(comments_all_labels_subject), "subject_predicted"=c(comments_all_pred_subject))

#Write a CSV file out with data from this run.
write.csv(tallyall, file = "SubjectsAll_Randomizer_567.csv")

```{r}
#Creates a data frame that compares predicted and actual labels for subject and structure
tally <- data.frame("text"=c(comments_rawVERB_R[7006:9340,]$text),"subject_label"=c(comments_test_labels_subject), "subject_predicted"=c(comments_test_pred_subject))

#Write a CSV file out with data from this run.
write.csv(tally, file = "Subjects_Randomizer_567.csv")

>>>>

---
title: "Naive Bayes Workflow Ver 2r.2b"
author: "Dan Johnson"
date: "2/14/2019"
output: html_document
---

@@

##Summary
This is **Version 2r.2b** of the basic workflow for classifying TA comments using a naive Bayes model. It pre-processes text using the same command set as Ver 2.0.b. The "r" designates this version has been modified to be able to randomize which rows are selected for training and test datasets. This updated version refines the final output tables so they are more informative.

Changes since 2a: this time I am trying out what happens if I go to ingroup/outgroup only, then run the ENTIRE dataset. I want to know how far off of my hand-coded table the RATIOS of effort are.

@@

##Version 2.r.2b of Naive Bayes (NB) Protocol

###Initial Data Input
```{r}
#Read in TA comments from CSV file.
base_dataVerYN <- read_csv(file='data/coded_full_comments_dataset_Spring18anonVERB.csv')
```

###Extract, Organize Data Subset
Extract comments and classification data subset
```{r}
#Select rows representing the sub-groups to compare. 
comments_subsetVerYN <- filter(base_dataVerYN,code.subject=="1_basic"|code.subject=="2_writing"|code.subject=="3_technical"|code.subject=="4_logic")

#Reduce larger dataframe to 3 required columns of data, and put columns in order needed.
comments_rawVerYN <- comments_subsetVerYN %>% select(23,24,22)

#Rename the columns.
names(comments_rawVerYN)[1] <- "subject"
names(comments_rawVerYN)[2] <- "structure"
names(comments_rawVerYN)[3] <- "text"

#This block uses 'forcats' to recode the Subject and Structure factors as either ingroup or outgroup.
#Changing this block is how I change and use other Subject and Structure factors as the ingroup.
#Looking ahead, could use this block and a variable name to simplify coding (NO, does not work).

comments_rawVerYN_V <- comments_rawVerYN %>% 
  mutate(subject = fct_recode(subject, ingroup = "3_technical", outgroup="1_basic", outgroup="2_writing", outgroup="4_logic"))

#%>% mutate(structure = fct_recode(structure, ingroup = "4_specific", outgroup="1_pointer",outgroup="2_copyedit",outgroup="3_general",outgroup="6_holistic",outgroup="7_idiomatic",outgroup="8_nobasis" ))
```

```{r}
#Change "subject" element from character to a factor for analysis.
comments_rawVerYN_V$subject <- factor(comments_rawVerYN_V$subject)
str(comments_rawVerYN_V$subject)
table(comments_rawVerYN_V$subject)
```

```{}
#Change "structure" element from character to a factor for analysis.
comments_rawVerYN_V$structure <- factor(comments_rawVerYN_V$structure)
str(comments_rawVerYN_V$structure)
table(comments_rawVerYN_V$structure)
```

```{r}
#Generate a vector of ~10,000 numbers (be sure it can be generated consistently)
#Adjust the number so it matches the number of rows in the original data frame
#Next, set the seed for random numbers, and randomize the order of the vector
vector <- 1:9340
set.seed(123) #change this seed value, and the data are randomized in a new sequence.
vector <- sample(vector)
glimpse(vector)
```

```{r}
#Append the vector as a new column to "comments_rawVerYN" with name "randomizer"
#Sort rows of dataframe according to "randomizer" column using dplyer 'arrange' function. 
comments_rawVerYN_V$randomizer <- c(vector)
comments_rawVerYN_R <-comments_rawVerYN_V %>% arrange(randomizer)
print(comments_rawVerYN_R)

@@

```{r}
#Convert text to all lower case letters.
comments_corpus_cleanVerYN_R <- tm_map(comments_corpusVerYN_R, content_transformer(tolower))

#Remove punctuation using the "removePunctuation" function. 
#This step removes evidence of questions, so may remove data.
comments_corpus_cleanVerYN_R <- tm_map(comments_corpus_cleanVerYN_R, removePunctuation)

#Remove numerals. 
#I am not sure this is beneficial; does it remove evidence indicating technical comments?
#comments_corpus_cleanVerYN_R <- tm_map(comments_corpus_cleanVerYN_R, removeNumbers)

#Stopword removal. 
#This is a standard cleanup step, but again may remove useful terms.
#The "stopwords" file is a convention; other files can be substituted for it
comments_corpus_cleanVerYN_R <- tm_map(comments_corpus_cleanVerYN_R, removeWords, stopwords())

@@

comments_dtm_1gram <- DocumentTermMatrix(comments_corpus_cleanVerYN_R, control=list(tokenize = NLP_Tokenizer))
comments_dtm_1gram_tidy <- tidy(comments_dtm_1gram)
inspect(comments_dtm_1gram)
```

@@

This code uses the comments in the order they are listed in the original file. Block for randomizing them was done earlier.
```{r}
comments_dtm_train <- comments_dtm_1gram[1:7005, ]
comments_dtm_test <- comments_dtm_1gram[7006:9340, ]
```

Save vectors labeling rows in the training and testing vectors
```{r}
comments_train_labels_subject <- comments_rawVerYN_R[1:7005, ]$subject
comments_test_labels_subject <- comments_rawVerYN_R[7006:9340,]$subject
```

```{}}
comments_train_labels_structure <- comments_rawVerYN_R[1:7005, ]$structure
comments_test_labels_structure <- comments_rawVerYN_R[7006:9340,]$structure
```

Make sure that the proportion of each sub-category is similar in the training and testing data sets.
```{r}
prop.table(table(comments_train_labels_subject))
prop.table(table(comments_test_labels_subject))
```

```{}
prop.table(table(comments_train_labels_structure))
prop.table(table(comments_test_labels_structure))
```

@@

Limit Document Term Matrix to only include words in the comments_freq_words vector. Using all the rows, but we want to limit the columns to these words in the frequency vector.
```{r}
comments_dtm_freq_train <- comments_dtm_train[ , comments_freq_words]
comments_dtm_freq_test <- comments_dtm_test[ , comments_freq_words]
```

The basic e1071 naive bayes classifier works with categorical features, so the matrix must be converted "yes" and "no" categorical variables. This is done using a **convert_counts function** and applying it to the data. This replaces values greater than 0 with yes, and values not greater than 0 with no. The resulting matrices have cells indicating "yes" or "no" if the word represented by the column appears in the text comment represented by the row.

```{r}
convert_counts2 <- function(x) {
  x <- ifelse(x > 0, "Yes", "No")
}

comments_train <- apply(comments_dtm_freq_train, MARGIN = 2, convert_counts2)
comments_test <- apply(comments_dtm_freq_test, MARGIN = 2, convert_counts2)
```

The alternate version below uses the original word frequencies without binarization.

```{}
# Function to KEEP word frequencies while still using the same variable names and code structure. The resulting matrices have cells with word frequencies instead.
convert_counts2 <- function(x) {
  y <- x
}

comments_train <- apply(comments_dtm_freq_train, MARGIN = 2, convert_counts2)
comments_test <- apply(comments_dtm_freq_test, MARGIN = 2, convert_counts2)
```

@@

###Train Model, Predict, Evaluate for Subject
This block uses the e1071 package to implement Naive Bayes algorithm on the data, and predict whether a message is likely to be in group 1_basic, 2_writing, 3_technical, or 4_logic. It evaluates the prediction with the actual data using a crosstable from the gmodels package.
```{r}
comments_classifier_subject <- naiveBayes(comments_train, comments_train_labels_subject, laplace=1)
comments_test_pred_subject <- predict(comments_classifier_subject, comments_test)

# Create a truth table by tabulating the predicted class labels with the actual class labels 
table("Predictions"= comments_test_pred_subject,  "Actual" = comments_test_labels_subject )
#table("Predictions2"= comments_test_pred_structure,  "Actual" = comments_test_labels_structure )

@@

# Prepare the confusion matrix. 
conf.mat <- confusionMatrix(comments_test_pred_subject, comments_test_labels_subject)

@@

```{r}
#Creates a data frame that compares predicted and actual labels for subject and structure
tally <- data.frame("text"=c(comments_rawVerYN_R[7006:9340,]$text),"subject_label"=c(comments_test_labels_subject), "subject_predicted"=c(comments_test_pred_subject))

#Write a CSV file out with data from this run.
write.csv(tally, file = "Subjects_InOut_Randomizer_123.csv")

### 2019-02-21 docs/hiding/Naive_bayes_V2yn.Rmd
update

```{r}
library(tidyverse)
library(tidytext)
library(tidyr)
library(tm)
library(SnowballC)
library(wordcloud)
library(e1071)
library(gmodels)
```

@@

##Version 2.0.r of Naive Bayes (NB) Protocol
###Initial Data Input
```{r}
#Read in TA comments from CSV file.
base_dataVerYN <- read_csv(file='data/coded_full_comments_dataset_Spring18anonVerYN.csv')
```

@@

@@

#Change "subject" element from character to a factor for analysis.
comments_rawVerYN$subject <- factor(comments_rawVerYN$subject)
str(comments_rawVerYN$subject)
table(comments_rawVerYN$subject)
```

```{r}
#Change "structure" element from character to a factor for analysis.
comments_rawVerYN$structure <- factor(comments_rawVerYN$structure)
str(comments_rawVerYN$structure)
table(comments_rawVerYN$structure)
```

@@

```{r}
#Append the vector as a new column to "comments_rawVerYN" with name "randomizer"
#Sort rows of dataframe according to "randomizer" column using dplyer 'arrange' function. 
comments_rawVerYN$randomizer <- c(vector)
comments_rawVerYN_R <-comments_rawVerYN %>% arrange(randomizer)
print(comments_rawVerYN_R)

@@

###Train Model, Predict, Evaluate for Subject
This block uses the e1071 package to implement Naive Bayes algorithm on the data, and predict whether a message is likely to be in group 1_basic, 2_writing, 3_technical, or 4_logic. It evaluates the prediction with the actual data using a crosstable from the gmodels package.
```{r}
comments_classifier_subject <- naiveBayes(comments_train, comments_train_labels_subject)
comments_test_pred_subject <- predict(comments_classifier_subject, comments_test)
CrossTable(comments_test_pred_subject, comments_test_labels_subject, prop.chisq = FALSE, prop.t = FALSE, dnn = c('predicted', 'actual'))
```

The cross table lists how many of the predicted categories are in their correct categories. Adding diagonally and dividing by total count gives the percent accuracy at predicting subject.
```{r}
print("Overall subject accuracy")
(14+54+1318+28)/23.35  #Need to find a way to calculate this automatically. 
```

@@

```{r}
print("Overall structure accuracy")
(66+64+949+5+1)/23.35  #Need to find a way to calculate this automatically. 
```

>>>>

```{r}
library(tidyverse)
library(tidytext)
library(tidyr)
library(tm)
library(e1071)
library(gmodels)
```

@@

##Version 2.0.YN of Naive Bayes (NB) Protocol
###Initial Data Input
```{r}
#Read in TA comments from CSV file.
base_dataVerYN <- read_csv(file='data/coded_full_comments_dataset_Spring18anonVERB.csv')
```

@@

#Reduce larger dataframe to 3 required columns of data, and put columns in order needed.
comments_rawVerYN <- comments_subsetVerYN %>% select(23,24,22)

@@

#This block uses 'forcats' to recode the Subject and Structure factors as either ingroup or outgroup.
#Changing this block is how I change and use other Subject and Structure factors as the ingroup.
#Looking ahead, could use this block and a variable name to simplify coding (NO, does not work).

comments_rawVerYN_V <- comments_rawVerYN %>% 
  mutate(subject = fct_recode(subject, ingroup = "3_technical", outgroup="1_basic", outgroup="2_writing", outgroup="4_logic")) %>% 
  mutate(structure = fct_recode(structure, ingroup = "4_specific", outgroup="1_pointer",outgroup="2_copyedit",outgroup="3_general",outgroup="6_holistic",outgroup="7_idiomatic",outgroup="8_nobasis" ))
```

***
POINT OF CONCERN ABOUT CODING
***
Doing multiple comments for a larger group like Structure is tedious. This block of code:
```
comments_rawVerYN_V <- comments_rawVerYN %>% 
    mutate(structure = fct_recode(structure, ingroup = "4_specific", outgroup="1_pointer",outgroup="2_copyedit",outgroup="3_general",outgroup="6_holistic",outgroup="7_idiomatic",outgroup="8_nobasis" ))
```
Has two issues. 
1. Each item being recoded as outgroup has to be typed in individually. If I try to enter multiple items in a list (either by embedding the list in a variable, or by concatenating the items to all be recoded as 'outgroup'), I get an error message saying you cannot apply fct_recode to more than one pair of items. Seems to be a lot of code to write to recode several variables to the same name.

2. This block was suggested, but is for writing the summary list of who gets COUNTED HOW; it does not affect the actual coding. 
```
partyid2 <- fct_collapse(gss_cat$partyid,
  missing = c("No answer", "Don't know"),
  other = "Other party",
  rep = c("Strong republican", "Not str republican"),
  ind = c("Ind,near rep", "Independent", "Ind,near dem"),
  dem = c("Not str democrat", "Strong democrat")
)
```
I do not want to collapse the COUNTS values together, I want to recode multiple variables simultaneously. I want to choose ALL of the NON-INGROUP items with one command and not add them individually. This is pseudo-code describing what I want to do:

```{}
comments_rawVerYN %>%
  mutate(subject = fct_recode(subject, ingroup = "3_technical", outgroup= ANYTHING_BUT "3_technical"))
```

3. Other suggestions I found:

```
https://community.rstudio.com/t/quickly-recoding-large-ish-vectors-in-a-tibble/2447

# object to decode and the key

tbl <- tibble(CODE = sample(letters[1:3], 1e+06, replace = TRUE))

key <- tribble(~CODE,   ~FRUIT, 
                 "a",  "apple", 
                 "b", "banana", 
                 "c",  "cherry"
               )

# Alternative One: dplyr::recode (what I used above basically)

mutate(tbl, FRUIT = recode(CODE, a = "apple", b = "banana", c = "cherry")) 
#> # A tibble: 1,000,000 x 2
#>     CODE  FRUIT
#>    <chr>  <chr>
#>  1     c cherry
#>  2     b banana
#>  3     a  apple
#>  4     b banana
#>  5     c cherry
#>  6     c cherry
#>  7     b banana
#>  8     c cherry
#>  9     a  apple
#> 10     a  apple
#> # ... with 999,990 more rows

# Alternative Two: named vector

# create a named vector from the key object and use it to recode
named_vector <- 
    key %>% 
    pmap(~set_names(..2, ..1)) %>% 
    unlist()

mutate(tbl, FRUIT = named_vector[CODE])
#> # A tibble: 1,000,000 x 2
#>     CODE  FRUIT
#>    <chr>  <chr>
#>  1     c cherry
#>  2     b banana
#>  3     a  apple
#>  4     b banana
#>  5     c cherry
#>  6     c cherry
#>  7     b banana
#>  8     c cherry
#>  9     a  apple
#> 10     a  apple
#> # ... with 999,990 more rows

left_join(tibblename, key)

benchmark(left_join(tbl, key, by = "CODE"), 
          columns = c("replications", "elapsed", "relative", "user.self", "sys.self"))

tbl <- tibble(CODE = sample(letters[1:3], 1e+06, replace = TRUE))

rev <- tbl %>%
  mutate(type =
           case_when(
             CODE == "a" ~ "apple",
             CODE == "b" ~ "banana",
             CODE == "c" ~ "cherry",
             FALSE ~ "no fruit"
           )
)

tbl <- tibble(CODE = sample(letters[1:3], 1e+06, replace = TRUE))

key <- tribble(~CODE,   ~FRUIT, 
               "a",  "apple", 
               "b", "banana", 
               "c",  "cherry"
)

tbl_with_factor <- mutate(tbl, CODE = as.factor(CODE))
key_with_factor <- mutate(key, CODE = as.factor(CODE))

***

```{r}
#Change "subject" element from character to a factor for analysis.
comments_rawVerYN_V$subject <- factor(comments_rawVerYN_V$subject)
str(comments_rawVerYN_V$subject)
table(comments_rawVerYN_V$subject)
```

```{r}
#Change "structure" element from character to a factor for analysis.
comments_rawVerYN_V$structure <- factor(comments_rawVerYN_V$structure)
str(comments_rawVerYN_V$structure)
table(comments_rawVerYN_V$structure)
```

@@

```{r}
#Append the vector as a new column to "comments_rawVerYN" with name "randomizer"
#Sort rows of dataframe according to "randomizer" column using dplyer 'arrange' function. 
comments_rawVerYN_V$randomizer <- c(vector)
comments_rawVerYN_R <-comments_rawVerYN_V %>% arrange(randomizer)
print(comments_rawVerYN_R)

@@

###Train Model, Predict, Evaluate for Subject
This block uses the e1071 package to implement Naive Bayes algorithm on the data, and predict whether a message is likely to be in group 1_basic, 2_writing, 3_technical, or 4_logic. It evaluates the prediction with the actual data using a crosstable from the gmodels package.
```{}
comments_classifier_subject <- naiveBayes(comments_train, comments_train_labels_subject)
comments_test_pred_subject <- predict(comments_classifier_subject, comments_test)
CrossTable(comments_test_pred_subject, comments_test_labels_subject, prop.chisq = FALSE, prop.t = FALSE, dnn = c('predicted', 'actual'))
```

The cross table lists how many of the predicted categories are in their correct categories. Adding diagonally and dividing by total count gives the percent accuracy at predicting subject.
```{r}
print("Overall subject accuracy")
(772+1174)/23.35  #Need to find a way to calculate this automatically. 
```

@@

```{r}
print("Overall structure accuracy")
(1117+592)/23.35  #Need to find a way to calculate this automatically. 
```

### 2019-02-21 docs/hiding/Random_forest_demo.Rmd
update

---
title: "Multinomial Naive Bayes Workflow Ver 3.0.b."
author: "Dan Johnson"
date: "2/13/2019"
output: html_document
---

@@

##Summary
This is an alternative version of my basic NB workflow for classifying TA comments. The code is slightly different than what was used for Categorical NB testing, but takes in text using the same command set as NB-Ver 2.0. It is based on a tutorial located here:
[https://rpubs.com/cen0te/naivebayes-sentimentpolarity]

This alternative code allows for true multinomial analysis, by switching between using binary yes/no categorization of words' presence or absence, and the actual frequencies. There is a trade-off though; to use non-categorical values, I can only have 2 assignment bins: in-group versus out-group. If I use multiple groups, the data fail to parse correctly. If I want to look at multiple classification bins at the same time, I have to use the categorical values method.

The point seems moot overall, since categorical NB seems to perform better than true multinomial NB. For both Subject and Structure, I reach 75-84% overall accuracy if I sort comments into ingroup/outgroup categories using binary (yes/no) word frequencies. Accuracy drops to ~65% if I use the raw numeric frequencies. Changing the Laplace value does not affect overall performance.

Naive Bayes permutations seem to plateau at 80-85%, regardless of permutations.

@@

```{r}
library(tm)
library(RTextTools)
library(e1071)
library(dplyr)
library(caret)
library(doMC)
registerDoMC(core=detectCores())

library(quanteda)
library(RColorBrewer)
library(ggplot2)

#library(tidyverse) 
#library(tidytext)
#library(tidyr)
```

##Version 3.0.b of Naive Bayes (NB) Protocol
###Initial Data Input
```{r}
#Read in TA comments from CSV file. 
#For convenience, I am reading in a shorter CSV file created previously using ver.2.0 code. This CSV file only lists 
#whether a comment is in or out of the 2 main groups, "Subject:3_technical" and "Structure:4_specific"

subset_M <- read.csv("/Users/danjohnson/Dropbox/Coding_Tools/R_Environment/R_Projects/ta_comments_FLC/comments_binary.csv", stringsAsFactors=FALSE)
glimpse(subset_M)
```
```{r}
set.seed(2012) #Randomizer
subset_M <- subset_M[sample(nrow(subset_M)), ]
glimpse(subset_M)
```

```{r}
text.corpus<-corpus(subset_M$text)
docvars(text.corpus)<-subset_M$subject
glimpse(text.corpus)
```

>>>>

---
title: "Demo of Random Forest Method Ver 1.0.a."
author: "Dan Johnson"
date: "2/13/2019"
output: html_document
---

@@

##Summary
This is testing the random forest method described here:
[https://datascienceplus.com/random-forests-in-r/]

@@

```{r}
#library(randomForest) #tools
#library(RTextTools) #demo data. Package which contains the Boston housing dataset
#library(MASS)
attach(Boston)
set.seed(101)

dim(Boston)
```

```{r}
#training Sample with 300 observations
train=sample(1:nrow(Boston),300)
#?Boston  #to search on the dataset

Boston.rf=randomForest(medv ~ . , data = Boston , subset = train)
Boston.rf
```

```{r}
plot(Boston.rf)
```

```{r}
oob.err=double(13)
test.err=double(13)

#mtry is no of Variables randomly chosen at each split
for(mtry in 1:13) 
{
  rf=randomForest(medv ~ . , data = Boston , subset = train,mtry=mtry,ntree=400) 
  oob.err[mtry] = rf$mse[400] #Error of all Trees fitted

  pred<-predict(rf,Boston[-train,]) #Predictions on Test Set for each Tree
  test.err[mtry]= with(Boston[-train,], mean( (medv - pred)^2)) #Mean Squared Test Error

  cat(mtry," ") #printing the output to the console

}
```

```{r}
test.err
oob.err
matplot(1:mtry , cbind(oob.err,test.err), pch=19 , col=c("red","blue"),type="b",ylab="Mean Squared Error",xlab="Number of Predictors Considered at each Split")
legend("topright",legend=c("Out of Bag Error","Test Error"),pch=19, col=c("red","blue"))
```
